Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-04 manuscript/manuscript.tex
ms updates

We've calculated the convergent correlation for all rows of the replicate
covariance matrices. Like temporal covariances, we visualize these through time
(Figure \ref{fig:figure-2} A), with each line representing the convergent
correlation from a particular reference generation $s$ as it varies with $t$
(shown on the x-axis). In other words, each of the colored lines corresponds to
the like-colored row of the convergence correlation matrix (upper left in
Figure \ref{fig:figure-2} A). We find these convergent covariances are
relatively weak, and decay very quickly from an initial value of about 0.1
(95\% block bootstrap confidence intervals $[0.094, 0.11]$) to around 0.01
(95\% CIs [0.0087, 0.015]) within 20 generations. This suggests that while
a reasonable fraction of the initial response is shared over the replicates,
this is followed by a rapid decay, a result consistent with the primary
finding of the original \textcite{Barghi2019-qy} study: that alternative loci
contribute to longer term adaptation across the different replicates.

@@

>>>>

We've calculated the convergent correlation for all rows of the replicate
covariance matrices. Like temporal covariances, we visualize these through time
(Figure \ref{fig:figure-2} A), with each line representing the convergent
correlation from a particular reference generation $s$ as it varies with $t$
(shown on the x-axis). In other words, each of the colored lines corresponds to
the like-colored row of the convergence correlation matrix (upper left in
Figure \ref{fig:figure-2} A). We find these convergent \vb{correlation
coefficients} are relatively weak, and decay very quickly from an initial value
of about 0.1 (95\% block bootstrap confidence intervals $[0.094, 0.11]$) to
around 0.01 (95\% CIs [0.0087, 0.015]) within 20 generations. This suggests
that while a reasonable fraction of the initial response is shared over the
replicates, this is followed by a rapid decay, a result consistent with the
primary finding of the original \textcite{Barghi2019-qy} study: that
alternative loci contribute to longer term adaptation across the different
replicates.

@@

\subsection{Forward-in-time Simulations}
